```{r}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, magrittr)
```

# Relation between extreme poverty rate and capital, labor and technology contributions to the economic growth by continents

## (a) Importing data frames

```{r}
poverty <- read_csv("https://raw.githubusercontent.com/gafnts/global-growth-accounting/main/regions_poverty.csv")
growth <- read_csv("https://raw.githubusercontent.com/gafnts/global-growth-accounting/main/regions_growth.csv")
```

## (b) Solow decomposition function

```{r}
solow <- function(data, y, l, k, labsh) {
  data %>%
  mutate(
    # Logs of output, capital and labor
    y = log({{y}}),
    k = log({{k}}),
    l = log({{l}}),
    # First differences (growth rates)
    dy = ({{y}} - lag({{y}})) * 100,
    dk = ({{k}} - lag({{k}})) * 100,
    dl = ({{l}} - lag({{l}})) * 100,
    # Share of capital in the economy
    capsh = 1 - {{labsh}},
    # Contributions of factors in the output growth
    k_cont = dk * capsh,
    l_cont = dl * {{labsh}},
    tfp_cont = dy - k_cont - l_cont
  ) %>%
  na.omit()
}
```

## (c) Transformations

```{r}
# Solow decomposition by region
regions_solow <- 
  growth %>%
  group_by(region) %>%
  filter(year %in% c(1984:2019)) %>%
  solow(y = y,
        l = l,
        k = k,
        labsh = labsh) %>%
  select(region, year, k_cont, l_cont, tfp_cont)

# Join dataframes
data <- 
  regions_solow %>% 
  left_join(poverty) %>% 
  select(region:tfp_cont, pov) %>% 
  ungroup()
```

## (d) Exploratory data analysis

```{r}
library(plotly)

lines <- function(data, x, y, color) {
  p <- 
    data %>%
    ggplot(aes({{x}}, {{y}}, color = {{color}})) +
    geom_line() 
  ggplotly(p)
}

poverty %>% lines(year, pov, region)
```

## (d) Pooled OLS

```{r}
library(panelr)
library(plm)
library(broom)
library(stargazer)

# Declare data frame as panel data
panel  <-  panel_data(data, id = region, wave = year)
```

```{r}
library(GGally)

ggpairs(panel)
```

```{r}
# Model 1: Pooled OLS
pooled <- plm(pov ~ k_cont + l_cont + tfp_cont, 
             data = panel,
             model = "pooling")

# Tidy summary
pooled %>% summary()

# Table
stargazer(pooled, type = "text")
```

Por hacer: Generar pruebas estadísticas, supervisar países por región en ambas bases de datos, redactar metodología, generar una gráfica para pobreza.

```{r}
data %>% 
  filter(region == "Europa") %>% 
  lm(pov ~ k_cont + l_cont + tfp_cont, data = .) %>% 
  summary()
```
